A Comparative Quality Metric for Fuzzing with Logic State Coverage

### 2024-02-28 paper/main.tex
discussion: semantic
lscov-llvm-pass: ignore uncond branches and sancov // lscov-llvm-rt: some reliability issues

\autoref{e:count} comes with three major benefits. First, it offers one of the
best accuracy among all alternatives (c.f., only 4\% error even in an extreme
filter density of 90\%) \cite{harmouch2017cardinality}. 
%, while its error rate is \emph{inversely proportional} to the actual number of
%elements in the set (i.e., even \emph{less} error as logic state coverage
%grows) \cite{harmouch2017cardinality}. 
%
Second, it allows for a near-constant-time calculation as it only requires the
number of 1s apart from the formula calculation, as well as empirically shown in
\cite{harmouch2017cardinality} (\textbf{R2}). 
%
Finally, it presents a calculable error bound that the actual number of elements
likely falls within given a confidence probability \cite{papapetrou2010cardinality}.

@@

\pp{Semantically abnormal behaviors}
%
While the definition of program behaviors is separated from the output, it can
still incorporates \emph{semantically} abnormal behaviors (i.e., semantic bugs)
by means of exceptions. To be specific, semantic error detection such as
semantic sanitizers \cite{kim2019hydra,yun2016apisan} may capture semantic bugs
on the fly and make the behavior abnormal by terminating it. The definition
allows this as exceptions reference the data context before it is revealed to
the output.

>>>>

\autoref{e:count} comes with three major benefits. First, it offers one of the
best accuracy among all alternatives (c.f., only 4\% error even in an extreme
filter density of 90\%)
\cite{harmouch2017cardinality,papapetrou2010cardinality}. 
%, while its error rate is \emph{inversely proportional} to the actual number of
%elements in the set (i.e., even \emph{less} error as logic state coverage
%grows) \cite{harmouch2017cardinality}. 
%
Second, it allows for a near-constant-time calculation as it only requires the
number of 1s apart from the formula calculation, as well as empirically shown in
\cite{harmouch2017cardinality} (\textbf{R2}). 
%
Finally, it presents a calculable error bound that the actual number of elements
likely falls within given a confidence probability \cite{papapetrou2010cardinality}.

@@

\pp{Semantically abnormal behaviors}
%
While the definition of program behaviors is separated from the output, it can
still incorporates \emph{semantically} abnormal behaviors (i.e., semantic bugs)
by means of exceptions. To be specific, semantic error detection such as
semantic sanitizers \cite{kim2019hydra,yun2016apisan} may capture semantic bugs
on the fly and make the behavior abnormal by terminating it. The definition
allows this because the output is just an observable subset of the data context
during the execution, which exceptions can reference at runtime.
